---
title: "S3 Tour Brittania"
output: 
  flexdashboard::flex_dashboard:
    theme:
      version: 4
      bootswatch: default
      navbar-bg: "#101010"
    logo: /www/ART-navbar.png
    orientation: rows
    vertical_layout: fill
    self_contained: false
---

```{css}
.datatables.html-widget.html-widget-static-bound { 
  height: auto !important;
  width: 90vw !important;
}
.dataTables_scrollBody {
  height: unset !important;
}

.value-box .icon i {
  position: absolute;
  top: 15px;
  right: 15px;
  font-size: 80px;
  color: rgba(255, 0, 0, 0.75);
}

```

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(here)
library(knitr)
library(lubridate)
library(DT)
library(plotly)
library(bslib)

load(here("data", "s3_tour_britannia", "data.RData"))

```

```{r}

stage_profile <- tibble(
  Stage = 1:8,
  Distance = c(48,67,27,48,33,41,54,55),
  Climbing = c(645,750,512,560,612,512,1250,999),
  Stage_name = c("R-1", "R-2", "R-3", "R-4", "R-5", "R-6", "R-7", "R-8")
)


riders_ART <- rider_list |> filter(Club == "ART")

max_races <- max(rider_list$Tour_races)

total_racing_riders <- riders_ART |> filter(Tour_races > 0) |> nrow()
total_races <- sum(riders_ART$Tour_races)
total_full_tour_riders <- riders_ART |> filter(Tour_races == max_races) |> nrow()


current_position_mixed <- results_list$race_league_mixed |> 
  filter(Team == "ART Racing") |> 
  select(Position) |> sum()
current_position_men <- results_list$race_league_gender |> 
  filter(Team == "ART Racing", gender == "M") |> 
  select(Position) |> sum()
current_position_women <- results_list$race_league_gender |> 
  filter(Team == "ART Racing", gender == "F") |> 
  select(Position) |> sum()


total_riders_by_category <- rider_list |>
  filter(Tour_races > 0) |>
  group_by(FRHC_tour, Gender) |>
  summarise(count = n(), .by = NULL, .groups = "drop") |>
  pivot_wider(names_from = FRHC_tour, values_from = count, values_fill = 0) |>
  mutate(Team = "ALL teams") |>
  select(Team, Gender, CAP, DRA, CRP, GHT, HAB, BON, CAY, JLP, PEP) |>
  arrange(desc(Gender)) |>
  filter(Gender %in% c("M", "F"))


riders_by_category <- riders_ART |>
  filter(Tour_races > 0) |>
  group_by(FRHC_tour, Gender) |>
  summarise(count = n(), .by = NULL, .groups = "drop") |>
  add_row(FRHC_tour = "CAP", Gender = "M", count = 0) |>
  add_row(FRHC_tour = "DRA", Gender = "M", count = 0) |>
  add_row(FRHC_tour = "CRP", Gender = "M", count = 0) |>
  add_row(FRHC_tour = "GHT", Gender = "M", count = 0) |>
  add_row(FRHC_tour = "HAB", Gender = "M", count = 0) |>
  add_row(FRHC_tour = "BON", Gender = "M", count = 0) |>
  add_row(FRHC_tour = "CAY", Gender = "M", count = 0) |>
  add_row(FRHC_tour = "JLP", Gender = "M", count = 0) |>
  add_row(FRHC_tour = "PEP", Gender = "M", count = 0) |>
  group_by(FRHC_tour, Gender) |>
  summarise(count = sum(count), .by = NULL, .groups = "drop") |>
  pivot_wider(names_from = FRHC_tour, values_from = count, values_fill = 0) |>
  mutate(Team = "ART only") |>
  select(Team, Gender, CAP, DRA, CRP, GHT, HAB, BON, CAY, JLP, PEP) |>
  arrange(desc(Gender))

riders_comparison_summary <-
  bind_rows(riders_by_category, total_riders_by_category)

ART_rider_table <-
  results_list$GC_time_least |>
  mutate( art_rider = str_detect(Rider, "\\[ART\\]$")) |>
  filter(art_rider == TRUE) |>
  left_join(results_list$GC_overall, by = c("Rider", "Stages", "Time")) |>
  mutate(
    `Pos (FHRC)` = Position.x,
    `Pos (overall)` = Position.y,
    Time = parse_time(Time, "%H:%M:%S"),
    `Gap (FHRC)` = Gap.x,
    `Gap (overall)` = Gap.y,
    ) |>
  select(`Pos (FHRC)`, `Pos (overall)`, Rider, category, gender, Stages, Time, `Gap (FHRC)`, `Gap (overall)`)

total_time_raced <- sum(ART_rider_table$Time) |>  as.period(unit = "%H:%M:%S")

ART_riders_stage_breakdown <-
  results_list$all_stage_performance |>
  mutate( art_rider = str_detect(Rider, "\\[ART\\]$")) |>
  filter(art_rider == TRUE) |>
  left_join(stage_profile, by = c("Stage"))

ART_league_results <-
  results_list$team_stage_result |>
  left_join(stage_profile, by = c("Stage" = "Stage_name")) |>
  filter(is.na(`Team league points`) == FALSE) |>
  mutate(art_rider = str_detect(Rider, "^ART")) |>
  filter(art_rider == TRUE)

team_stage_summary <-
  results_list$team_stage_result |>
  filter(is.na(`Team league points`) == FALSE) |>
  mutate(
    team = str_extract(Rider, "^[:alpha:]+"),
    stage_num = as.integer(str_extract(Stage, "[:digit:]+"))
  ) |>
  mutate(art_team = str_detect(Rider, "^ART")) |>
  group_by(team) |>
  mutate(
    cumulative_points_raw = cumsum(`Team points raw`),
    cumulative_league_points = cumsum(`Team league points`),
    art_cumulative_points_raw = case_when(art_team == TRUE ~ cumulative_points_raw, TRUE ~ NA),
    art_cumulative_league_points = case_when(art_team == TRUE ~ cumulative_league_points, TRUE ~ NA)
  )
  
  

```



Summary statistics
======================

> Tour series 3 - Tour France - Last updated: `r last_updated` 

Row
------------------------
### team position (mixed)
```{r}
valueBox(current_position_mixed, icon = "fa-ranking-star", color = "#101010")
```

### team position (men)
```{r}
valueBox(current_position_men, icon = "fa-ranking-star", color = "#101010")
```

### team position (women)
```{r}
valueBox(current_position_women, icon = "fa-ranking-star", color = "#101010")
```

Row
------------------------
### riders have raced
```{r}
valueBox(total_racing_riders, icon = "fa-people-group", color = "#101010")
```

### stages raced
```{r}
valueBox(total_races, icon = "fa-person-biking", color = "#101010")
```

### riders have raced all stages
```{r}
valueBox(total_full_tour_riders, icon = "fa-trophy", color = "#101010")
```

Row
------------------------
### time spent racing
```{r}
valueBox(
  paste0(total_time_raced@day, "d ",total_time_raced@hour, "h"), 
  icon = "fa-stopwatch", color = "#101010")
```

### km ridden
```{r}
valueBox(format(sum(ART_riders_stage_breakdown$Distance), big.mark = ","), icon = "fa-road", color = "#101010")
```

### m climbed
```{r}
valueBox(
  format(sum(ART_riders_stage_breakdown$Climbing), big.mark = ",", scientific = FALSE), 
  icon = "fa-mountain-sun", color = "#101010")
```


Team riders
======================

### ART riders
```{r}
ART_rider_table |>
  DT::datatable(
    style = "auto",
    rownames = FALSE,
    options = list(
      initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
        "}"),
      pageLength = -1,
      dom = 'ft',
      order = list(1, 'asc')
    ))
```


Participation stats
======================

### How many ART riders rode each stage?
```{r}
ART_riders_by_stage <-
  ART_riders_stage_breakdown |>
  group_by(Stage) |>
  summarise(num_riders = n(), .groups = "drop")

ART_riders_by_stage |>
  ggplot(mapping = aes(x = Stage, y = num_riders, fill = Stage)) +
  theme_linedraw() +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = num_riders), vjust = 1.5, colour = "white") +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8))
```

### How many stages has each ART rider ridden?
```{r}
ART_riders_total_stages <-
  ART_rider_table |>
  group_by(Stages) |>
  summarise(num_riders = n(), .groups = "drop")
  
ART_riders_total_stages |>
  ggplot(mapping = aes(x = (Stages), y = num_riders, fill = (Stages))) +
  theme_linedraw() +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = num_riders), vjust = 1.5, colour = "white") +
  scale_x_continuous(breaks = c(1,2,3,4,5,6,7,8))
  
```


Raw points
======================

### How many raw points has ART earned each stage?
```{r}
ART_league_results |>
  ggplot(mapping = aes(x = Stage, y = `Team points raw`, fill = Stage.y)) +
  theme_linedraw() +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = `Team points raw`), vjust = 1.5, colour = "white")
```

### ART cumulative raw points vs other teams
```{r}
team_stage_summary |>
  ggplot(mapping = aes(x = Stage, y = cumulative_points_raw, group = team)) +
  theme_linedraw() +
  geom_line(color = "grey90")+
  geom_line(mapping = aes(x = Stage, y = art_cumulative_points_raw, group = team))

```


League points
======================

### How many league points has ART earned each stage? (Max 50)
```{r}
ART_league_results |>
  ggplot(mapping = aes(x = Stage, y = `Team league points`, fill = Stage.y)) +
  theme_linedraw() +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = `Team league points`), vjust = 1.5, colour = "white")
```


### ART cumulative league points vs other teams
```{r}
team_stage_summary |>
  ggplot(mapping = aes(x = Stage, y = cumulative_league_points, group = team)) +
  theme_linedraw() +
  geom_line(color = "grey90")+
  geom_line(mapping = aes(x = Stage, y = art_cumulative_league_points, group = team))
```


